Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-14 paper/sheaf_lics.tex
redistribute section II

@@

The idea is then to define sheaves in $\E$ as objects of $\E$ for
which it is impossible to make a distinction between objects and their
dense subobjects. This idea is formalized by saying that for every
dense subobject $A$ of $E$, the following canonical map is an
isomorphism
%
\begin{equation}\label{equ:sheaf_def}
\Hom{\E}(E,F) \rightarrow \Hom{\E}(A,F).
\end{equation}
%
On can show that $\Sh{\E}$, the full sub-category of $\E$ given by
sheaves, is again a topos, with classifying object
%
$$
\Omega_j = \{ P \in \E \ | \ j P  \leftrightarrow P \}.
$$
%
Thus, in case of the double negation, the resulting topos is boolean  
and admits classical reasoning.

@@

\subsection{Plan of the Paper}
\begin{itemize}
\item Section~\ref{sec:hott}, we define the foundations on which
  our worked is based.
\item Section~\ref{sec:sheaves}, we explain the construction of the
  sheafification functor.
\item Section~\ref{sec:formalization} presents the details of the
  formalization in Coq.
\item Finally, we present future works.
\end{itemize}

@@

\subsection{Homotopy Type Theory}
\label{ssec:hott}

@@

\subsection{Left exact Modalities}
\label{sec:lexmod}

\nt{
To be checked:
  Condition iv of Thm 7.7.5 of HoTT
}

@@

A left exact modality leads to a new theory with new principles. A
basic example is the {\em open modality of $P$} for a $P:\HProp$, $\modal_P T = P \to T$. 
When one works in the subuniverse defined by this modality, defining
an inhabitant of a type $T$ is actually giving an inhabitant of $P \to
T$. Thus, being in this subuniverse is just adding the axiom $P$ to
the theory. Sadly, adding an axiom this way does not add any
computational content to $P$, thus is not completely satisfactory.

@@

\subsection{Generalized pullbacks}
\label{sec:gener-pb}
\kq{Do we keep this name ?}

In homotopy type theory, we have 
$$X\times_Y \cdots\times_Y X = \sum_{x:X^n} (f x_1 = f x_2) \land
\cdots \land (f x_{n-1} = f x_n).$$
\begin{defi}
  If $f:X \to Y$ is a map, then the {\em \v{C}ech nerve} of $f$ is the
  diagram
  $$\xymatrix{
    C(f) := \cdots~ X \times_Y X \times_Y X \tar[r]{4pt} & X \times_Y X \dar[r]{2pt} & X
  }$$
with canonical projections.
\end{defi}

>>>>

 \IEEEpubid{}

@@

The idea is then to define sheaves in $\E$ as objects of $\E$ for
which it is impossible to make a distinction between objects and their
dense subobjects. This idea is formalized by saying that for every
dense subobject $A$ of $E$, the following canonical map is an
isomorphism
%
\begin{equation}\label{equ:sheaf_def}
\Hom{\E}(E,F) \rightarrow \Hom{\E}(A,F).
\end{equation}
%
On can show that $\Sh{\E}$, the full sub-category of $\E$ given by
sheaves, is again a topos, with classifying object
%
$$
\Omega_j = \{ P \in \E \ | \ j P  = P \}.
$$
%
Thus, in case of the double negation, the resulting topos is boolean  
and admits classical reasoning.

@@

\subsection{Plan of the Paper}

Section~\ref{sec:hott} defines the foundations of homotopy type theory
and the definition of modalities, on which this paper is based.
%
Section~\ref{sec:sheaves} defines the notion of sheaves in homotopy
type theory.
%
Section~\ref{sec:sheafification} depicts the construction of the
sheafification functor.
%
Section~\ref{sec:formalization} presents the details of the
  formalization in Coq.
%
Finally, Section~\ref{sec:future-works} concludes on future works.

@@

In this section, we review some basic definitions in homotopy type
theory that are central in our formalization but not specific to
sheafification. 
%
Section~\ref{ssec:hott} introduces the notion of homotopy types and
classifying objects as defined in~\cite{sets_in_hott}.
%
Section~\ref{sec:colim-homot-type} introduces the notion of colimits
in homotopy type theory. 
%
And Section~\ref{sec:giraud-ax} defines (a particular case of)
Giraud's axiom on higher topoi that we need in the definition of
sheafification.

The definition of Section~\ref{ssec:hott} are part of the Coq library
available at \url{https://github.com/HoTT/HoTT}, while other definitions
and theorems are specific to our formalization.

 \subsection{Homotopy Types and Classifying Objects}
\label{ssec:hott}

@@

\subsection{Colimits in Homotopy Type Theory }
\label{sec:colim-homot-type}

\nt{Kevin -> complete this subsection}

Definition of graphs, diagrams, is\_colimit.

Maybe the HIT of colimit, at least say that using HIT, all colimits
exists.

\subsection{Giraud's axiom}
\label{sec:giraud-ax}

In homotopy type theory, we have 
$$X\times_Y \cdots\times_Y X = \sum_{x:X^n} (f x_1 = f x_2) \land
\cdots \land (f x_{n-1} = f x_n).$$
\begin{defi}
  If $f:X \to Y$ is a map, then the {\em \v{C}ech nerve} of $f$ is the
  diagram
  $$\xymatrix{
    C(f) := \cdots~ X \times_Y X \times_Y X \tar[r]{4pt} & X \times_Y X \dar[r]{2pt} & X
  }$$
where the arrows are the canonical projections.
\end{defi}

\section{Left exact Modalities}
\label{sec:lexmod}

\cite{shulman-higher-modalities}

\subsection{Definition}

@@

\subsection{Examples of Left Exact Modalities}

A basic example is the {\em open modality of $P$} for a $P:\HProp$,
$\modal_P T = P \to T$.  When one works in the subuniverse defined by
this modality, defining an inhabitant of a type $T$ is actually giving
an inhabitant of $P \to T$. Thus, being in this subuniverse is just
adding the axiom $P$ to the theory. Sadly, adding an axiom this way
does not add any computational content to $P$, thus is not completely
satisfactory.

@@

\subsection{The new type theory arising from a left exact modality}

A left exact modality leads to a new theory with new principles.
